\title{ROS2 for Robot Mapping and Navigation}
\author{
        Zoe Li \\
                Sunnyvale CA USA\\
}
\date{\today}

\documentclass[12pt]{article}
\renewcommand{\thesection}{\Roman{section}}
\begin{document}
\maketitle

\begin{abstract}
 This guide gives an overview of ROS2 status with an example of SLAM implementation. ROS2 is an upgrade after one decade since the introduction of ROS (Robotic Operating System) and is still under heavy development at this moment as June 2019. In this guide, we discuss and evaluate some of its new features by implementing SLAM in ROS2 in simulation and on a real robot. These new features are briefly introduced and some are tested in this implementation. A demo with source code is provided in the end of the paper.
\end{abstract}

\section{Introduction}
This is time for all good men to come to the aid of their party!

\paragraph{Outline}
The remainder of this article is organized as follows.
Section~\ref{previous work} gives account of previous work.
Our new and exciting results are described in Section~\ref{results}.
Finally, Section~\ref{conclusions} gives the conclusions.

\section{Related Work}\label{related Work}
A much longer \LaTeXe{} example was written by Gil~\cite{Gil:02}.

\section{Method}\label{method}
\section{Results}\label{results}
In this section we describe the results.

\section{Conclusions}\label{conclusions}
We worked hard, and achieved very little.

\section{Reference}\label{reference}
\bibliographystyle{abbrv}
\bibliography{main}

\end{document}